Extreme climatic events with asymmetric tail-dependence affect population-extinction risk

### 2019-07-15 MainText.Rmd
writing intro

<!--how common are the extreme events? 
what are the implication of extreme events on life history? 
any negative or positive effects? : past literatures-->
For past few decades, there have been evidences that anthropogenic climate change 
is causing more frequent extreme events [ref] (e.g. temperature or precipitation extremes,
heat-waves, wild-fire) which show shifts in its mean, 
in the variability of the distribution, as well as changes in its 
symmetry or skewness. Such extreme climatic events (ECE) can pose severe
impacts at the individual, population, community and ecosystem level (e.g. Parmesan,
Root & Willig 2000; van de Pol et al. 2010b; Hoover,
Knapp & Smith 2014). Therefore, understanding the long-term impacts of changes 
in ECEs has been a longstanding interest in ecological research, specically in modelling 
extreme-risks [ref:Risk Analysis, Vol. 32, No. 11, 2012].

<!--How extinction risk is related to extreme events : past studies
consequences of extreme events on population life history, community-->

>>>>

<!--how common are the extreme events?-->
For past few decades, there have been increasing evidences that anthropogenic climate change 
is causing extreme events, e.g. temperature or precipitation extremes,
heat-waves, wild-fire etc. [@ummenhofer2017extreme]. Frequent extreme events 
can shift temperature or precipitation-mean, 
change variability of the distribution, as well as change its 
symmetry or skewness. Such extreme climatic events (ECE) can pose severe
impacts at the individual, population, community and ecosystem level [@bragazza2008climatic; 
@gutschick2003extreme; @jiguet2011community; 
@hoover2014resistance]. Therefore, 
understanding the long-term impacts of changes 
in ECEs has been a longstanding interest in ecological research 
[@katz2005statistics; @smith2011ecological; @diez2012will; @moritz2013future; @bailey2016tackling].

<!--How extinction risk is related to extreme events : past studies
consequences of extreme events on population life history, community-->
Earlier studies showed ECEs may affect species abundances (species re-ordering) through 
life-history traits and this alteration in community structures could cascade 
through higher hierarchical levels and lead to local extinction of 
species [@thomas2004extinction; @edgar2010nino; @moreno2011extreme]. For example, 
a study based on annal survival data showed changes
in prey communities induced by extreme flooding affected predators in 
aquatic and adjacent riparian habitats [@chiu2013impact]. Similarly, 
$43$ years of ring-recovery data was used to examine the demographic impact of ECEs 
through temporal variability in juvenile, immature and adult survival
of European shags on the Isle of May in eastern Scotland [@frederiksen2008demographic].
A recent study [@mcdermott2017sensitivity] investigated the sensitivity 
of $41$ UK butterfly species to four different ECEs (extreme heat, extreme cold, 
extreme precipitation, drought) over $37$ years (1976-2012) at the site level, across 
each species' life-stages. Successive ECEs with short time intervals 
could weaken the resistance of plant communities too [@dreesen2014successive]. 
All these studies indicated that environmental stochasticity (through ECEs) 
can lead to demographic stochasticity (through influence on reproductive or 
mortality rate) of different stage class of a population making it vulnerable 
to local extinction.
